A Survey of Wearable Device Risk Perceptions

### 2015-01-05 wearables_survey.tex
addressing Serge's comments, added missing hlines for tables, minor formatting.

\subsection{Smartphones and Wearables Concerns}
%I really don't know what this first sentence means...

Designs to improve end-user security need to be grounded in user research to better understand end-user concerns. Felt \etal were among the first to examine the security concerns of smartphone users using a large-scale online survey~\cite{Felt}. Their survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges. Participants were asked how upset they would be if a certain action had occurred without their permission. Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).'' Our work builds upon this study, by aiming to evaluate the types of concerns that users have surrounding future wearable device capabilities, and then to compare those concerns to concerns surrounding more established technologies.

@@

%In total, the survey consisted of 367 unique questions, with each participant answering 27 questions. Out of the 27 seen by each participant, 17 of the questions were constant, whereas 10 of the questions were selected at random from larger sets of questions.

@@

\subsubsection{Smartphone Scenarios}

\label{sec:smartphones}

We presented participants with a second set of scenarios in order to control for the type of device being used. These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 304 <data> and <recipient> combinations, we created 5 questions based on the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}. We randomly presented participants with 2 of the following 5 questions: \\[-.8cm]

@@

\subsubsection{Risk and Benefit Assessment}

In addition to investigating reactions to particular scenarios, we also examined broad perceptions of various new technologies, and how those perceptions compared to other well-established technologies. To this end, we modeled this section of the survey after the seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which they asked participants to relatively rank several technologies by both their risk and benefit to society. We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity. We chose these technologies because they represented varying levels of risks and benefits.

@@

\subsection{Recruitment and Analysis Method}

We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk. We restricted participants to those over 18 years old, living in the United States, and having a successful HIT completion rate of 95\% or above. Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants. We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and one participant who was under 18, leaving us with a total sample size of 1,784. Of these, 55.10\% were male, with a median age of 29 ($\sigma$ = 10.37).

@@

\subsection{Concern Factors}

In this section, we discuss the factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable device or a smartphone. We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of these factors, including demographic traits.

@@

%SE: This doesn't add much, the numbers can be put in the text to save space.
%LL: Agreed.

%\begin{figure}
%	\centering
%	\includegraphics[width=0.5\textwidth]{recipient.png}
%	\caption{(This is a placeholder! TODO: generate a better plot for data recipient)}
%\end{figure}

@@

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| r | l | r |}
Rank & Data &  VUR  \\
\hline
1 & a video of you unclothed & 95.97\% \\
2 & bank account information & 95.91\% \\
3 & social security number & 94.84\% \\
4 & video of you entering in your PIN & 92.67\% \\
5 & a photo of you unclothed & 92.59\% \\
6 & an incriminating/embarrassing photo of you & 91.39\% \\
7 & username and password for websites & 89.55\% \\
8 & credit card information & 88.98\% \\
9 & an incriminating/embarrassing video of you & 88.41\% \\
10 & a random (inward-facing) photo you at home & 87.50\% \\
 & \vdots & \\
64 & eye movement patterns (for eye tracking) & 40.51\% \\
65 & when and how much you exercise  & 38.66\% \\
66 & when you are happy or having fun  & 34.75\% \\
67 & which television shows you watch & 30.20\% \\
68 & when you are busy or interruptible  & 29.50\% \\
69 & music from your device  & 28.06\% \\
70 & your heart rate & 27.50\% \\
71 & your age & 24.29\% \\
72 & the language you speak & 15.86\% \\
73 & your gender & 15.00\% \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

@@

\begin{table}%[h]
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
%All	2.814	0.1395	No		3589		0.001\\
%Q1	2.500	0.1139	No		714		0.004\\
%Q2	17.333	<0.0001	Yes		708		0.024\\
%Q3	0.020	0.8886	No		699		0.000\\
%Q4	1.426	0.2324	No		731		0.002\\
%Q5	1.611		0.2043	No		710		0.002\\

%SE: Can you add sample sizes to this table?
Question & $\chi^2$ & p-value & n & $\phi$ \\
\hline
All & 2.202 & <0.1378 & 3,588 & 0.001\\
Q1 & 2.500 & <0.1139 & 714 & 0.004\\
Q2 & 17.333 & <0.0001 & 708 &  0.024\\
Q3 & 0.020 & <0.8886 & 699 &  0.000\\
Q4 & 1.413 & <0.2345 & 730& 0.002\\
Q5 & 1.604 & <0.2054 & 709 & 0.002\\
\hline
\end{tabular}
\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
\label{betweendevice}
\end{center}
\end{table}

>>>>

\subsection{Smartphones and Wearables Concerns}
Designs to improve end-user security need to be grounded in user research to better understand end-user concerns. Felt \etal were among the first to examine the security concerns of smartphone users using a large-scale online survey~\cite{Felt}. Their survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges. Participants were asked how upset they would be if a certain action had occurred without their permission. Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).'' Our work builds upon this study, by aiming to evaluate the types of concerns that users have surrounding future wearable device capabilities, and then to compare those concerns to concerns surrounding more established technologies.

@@

@@

\subsubsection{Smartphone Scenarios}
\label{sec:smartphones}
We presented participants with a second set of scenarios in order to control for the type of device being used. These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 304 <data> and <recipient> combinations, we created 5 questions based on the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}. We randomly presented participants with 2 of the following 5 questions: \\[-.8cm]

@@

\subsubsection{Risk and Benefit Assessment}
In addition to investigating reactions to particular scenarios, we also examined broad perceptions of various new technologies, and how those perceptions compared to other well-established technologies. To this end, we modeled this section of the survey after the seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which they asked participants to relatively rank several technologies by both their risk and benefit to society. We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity. We chose these technologies because they represented varying levels of risks and benefits.

@@

\subsection{Recruitment and Analysis Method}
We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk. We restricted participants to those over 18 years old, living in the United States, and having a successful HIT completion rate of 95\% or above. Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants. We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and one participant who was under 18, leaving us with a total sample size of 1,784. Of these, 55.10\% were male, with a median age of 29 ($\sigma$ = 10.37).

@@

\subsection{Concern Factors}
In this section, we discuss the factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable device or a smartphone. We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of these factors, including demographic traits.

@@

@@

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| r | l | r |}
\hline
Rank & Data &  VUR  \\
\hline
1 & a video of you unclothed & 95.97\% \\
2 & bank account information & 95.91\% \\
3 & social security number & 94.84\% \\
4 & video of you entering in your PIN & 92.67\% \\
5 & a photo of you unclothed & 92.59\% \\
6 & an incriminating/embarrassing photo of you & 91.39\% \\
7 & username and password for websites & 89.55\% \\
8 & credit card information & 88.98\% \\
9 & an incriminating/embarrassing video of you & 88.41\% \\
10 & a random (inward-facing) photo you at home & 87.50\% \\
 & \vdots & \\
64 & eye movement patterns (for eye tracking) & 40.51\% \\
65 & when and how much you exercise  & 38.66\% \\
66 & when you are happy or having fun  & 34.75\% \\
67 & which television shows you watch & 30.20\% \\
68 & when you are busy or interruptible  & 29.50\% \\
69 & music from your device  & 28.06\% \\
70 & your heart rate & 27.50\% \\
71 & your age & 24.29\% \\
72 & the language you speak & 15.86\% \\
73 & your gender & 15.00\% \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

@@

\begin{table}%[h]
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
%All	2.814	0.1395	No		3589		0.001\\
%Q1	2.500	0.1139	No		714		0.004\\
%Q2	17.333	<0.0001	Yes		708		0.024\\
%Q3	0.020	0.8886	No		699		0.000\\
%Q4	1.426	0.2324	No		731		0.002\\
%Q5	1.611		0.2043	No		710		0.002\\
\hline
Question & $\chi^2$ & p-value & n & $\phi$ \\
\hline
All & 2.202 & <0.1378 & 3,588 & 0.001\\
Q1 & 2.500 & <0.1139 & 714 & 0.004\\
Q2 & 17.333 & <0.0001 & 708 &  0.024\\
Q3 & 0.020 & <0.8886 & 699 &  0.000\\
Q4 & 1.413 & <0.2345 & 730& 0.002\\
Q5 & 1.604 & <0.2054 & 709 & 0.002\\
\hline
\end{tabular}
\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
\label{betweendevice}
\end{center}
\end{table}
